---
title: "ma615"
author: "Luyin Fu"
date: "12/13/2019"
output:
  ioslides_presentation:
    widescreen: true
    transition: slower
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
pacman::p_load("ggplot2","plotly","knitr","dplyr","tidyr", "stringr", "tinytex","magrittr","kableExtra", "newsanchor", "tidytext", "wordcloud", "RColorBrewer")

#PLEASE download this package from github!
#OR part of the plots won't show up
#devtools::install_github("lchiffon/wordcloud2")
```




## What's up, San Francisco?
<div class="blue2">Catch up with San Francisco news at a glance.</div>

Using news API, I made a wordcloud of the most frequently appeared words in the most relevant news last month. The download limit is 100 items.

```{r, message=FALSE}

df <- get_everything(query = "san francisco", sort_by = "relevancy", page = 1, page_size = 100, api_key ="6572647b5bd941efa75620ffe1bfeca0")
# #from = "2019-11-14",
# #page = 1, page_size = 100, sort_by = "popularity",
# 
# df$results_df[[3]]

# title=df$results_df[2]
 description=df$results_df[[3]]
# author=df$results_df[1]
# id=df$results_df[8]
pal2 <- brewer.pal(8,"Dark2")
set.seed(8)

wordfreq=tibble(description) %>% 
  unnest_tokens(word, description) %>%
  anti_join(stop_words) %>%
  count(word, sort = TRUE)
wordcloud(wordfreq$word, freq = wordfreq$n, scale=c(6, 0.6), max.words = 80, rot.per = 0.25, colors = pal2, random.order=FALSE, vfont=c("serif","plain")) 
```

## What's going on in San Francisco? 

This is a wordcloud of most frequently appeared phrases. Some of the phrases that caught my attention are: 5G Service, Scooter Company, SanFrancisco startup, Administrative Leave

```{r}
library(wordcloud2)

description_bigrams=tibble(description) %>%
  unnest_tokens(bigram, description, token = "ngrams", n = 2) %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word) %>%
  count(word1, word2, sort = TRUE) %>%
  mutate(word=str_c(word1, word2, sep = " ")) %>%
  rename(freq=n) %>% 
  select(word, freq) %>%
  filter(freq>=2)

wordcloud2(description_bigrams, size =2, shape = 'pentagon', color = "random-light")
```

## Sentiments

Comparing the news to the AFFIN lexicon, we can assign sentiment value to words appearing in the news.
The sentiments of news coverage this week is pretty balanced

```{r, message=FALSE}
tibble(description) %>% mutate(id = row_number()) %>%
  unnest_tokens(word, description) %>%
  anti_join(stop_words) %>% 
  inner_join(get_sentiments("afinn")) %>%
  group_by(id) %>% mutate(sentment=sum(value)) %>% ungroup() %>%
  ggplot()+geom_density(aes(x=sentment), color="#FF99CC", fill="#FF99CC", alpha=0.5)

```


## Data Aquisation

Starting out with San Francisco film location data from (https://data.sfgov.org/Culture-and-Recreation/Film-Locations-in-San-Francisco/yitu-d5am), I downloaded the coordinates data using google API and the geocode function.

<div class="red2"> Now, lets explore film locations in San Francisco!</div>

```{r}
# This is the code I used to download coordinates data
# film=read.csv("Film_Locations_in_San_Francisco.csv")
# devtools::install_github("dkahle/ggmap")
# library(ggmap)
# 
# register_google(key = "AIzaSyBFs5oqwXv3ovQaKNbSqCLIe9sqAcpjvNo")
# 
# lonlat <- geocode(paste(as.character(film$Locations), " SF"))
# film_loc=cbind(film, lonlat)
# write.csv(film_loc, "film_loc.csv", row.names = FALSE)



# load film data
film_loc=read.csv("film_loc.csv")
film_loc %<>% 
  #unifying the names of production companies
  mutate(Production.Company=as.character(Production.Company)) %>%
  mutate(`Production Company`=ifelse(str_detect(Production.Company, "Columbia Pictures"), "Columbia Pictures Corp.", ifelse(str_detect(Production.Company, "Metro-Goldwyn"), "Metro-Goldwyn Mayor", ifelse(str_detect(Production.Company, "Orion Pictures"), "Orion Pictures Corp.", ifelse(str_detect(Production.Company, "PYM Particles"), "PYM Particles Production, LCC", ifelse(str_detect(Production.Company, "Twentieth Century Fox"), "Twentieth Century Fox Film Coorp.", ifelse(str_detect(Production.Company, "Warner Bro"), "Warner Bros. Pictures", Production.Company))))))) %>%
  select(-Production.Company)
```




## Film Locations in SF

Here's a sample of film locations in SF

```{r}
library(maps)
library(leaflet)
film_loc1=film_loc %>% drop_na(lon) %>% sample_n(25)
        #define icons for film shooting spots 
        icons1 <- awesomeIcons(
            icon = 'home',
            iconColor = 'rgba',
            library = 'fa', 
            markerColor = 'lightblue',
            squareMarker = F,
            spin=T
        )
        # create San Francisco Map
        leaflet(film_loc1) %>% #set the coordinates for San Francisco
            setView(-122.4194, 37.7749, zoom = 12) %>% 
            addProviderTiles("CartoDB.Positron", group = "Map") %>%
            addProviderTiles("Esri.WorldImagery", group = "Satellite")%>% 
            addProviderTiles("OpenStreetMap", group = "Mapnik") %>% 
            #add markers for the locations where the selected film was shot
            addAwesomeMarkers(~lon, ~lat, label = ~Title, icon = icons1) %>%
            addScaleBar(position = "bottomleft") 
            
```


## Production Companies

Production Companies that shot the largest quantity of movies in SF

```{r}
# create a table that shows the production company that shot the largest nbumber of films in San Francisco
film_loc %>% 
  group_by(`Production Company`, Title) %>%
  mutate(`number of films`=n()) %>% ungroup() %>%
  group_by(`Production Company`) %>% mutate(`First Year`=min(Release.Year)) %>%
  ungroup() %>% select(`Production Company`, `number of films`, `First Year`) %>% 
  distinct() %>% arrange(desc(`number of films`)) %>%
  slice(1:10) %>%
  kable(align = "c", booktabs = T) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = T, position = "center") %>%
  column_spec(2, width = "8em", background = "#56B4E9")%>%
  row_spec(0, angle = -25)

```

## Film names

Here are some of the films that have scenes shot in SF

```{r}
film_loc %>% select(Title, Release.Year, Distributor ) %>% 
  group_by(Title) %>% mutate(quantity=n()) %>% distinct() %>%
  ggplot()+
  aes(x=Release.Year, y=quantity, label = Title, color=Distributor)+
  geom_text(nudge_x = 0.25, nudge_y = 0.25, check_overlap = TRUE) + 
  theme(legend.position = "none")+
  labs(x="Release Year",
       y="Number of Scenes in SF",
       title = "Films shot in San Francisco")
  #scale_color_brewer(type = 'div', palette = 4, guide = FALSE) 
```


## Films

Films that shot most scenes in SF

```{r}
p2=film_loc %>% count(Title, sort = TRUE) %>% slice(1:10) %>%
  ggplot() +aes(x=Title, y=n)+geom_bar(stat = "identity", fill="#C3D7A4")+ coord_flip()+theme(legend.position = "none")
ggplotly(p2)
```



